D3064R0: Bringing the Laws of Physics, Computer-System Constraints, and Compilers to Bear on the OOTA Problem

### 2024-02-16 ootavacuous.tex
Reword hope for definition of semantic dependency
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
"Relative versus Absolute Dependency" s/compromising/restrictive/
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Semantic dependency is a notoriously difficult concept to define
rigorously and precisely.
A large part of the reason is because it was never a completely clear
concept to begin with, especially when there are multiple accesses to
the variables involved.
In this section we will stick our necks out by offering just such a
definition.
No doubt many people will object to it for various reasons, but we
hope it will provide a starting point for discussions that move the
entire field forward.

@@

A drawback of the definition is that it is only relative to a specific
compiler or implementation.
This may strike some people as too compromising, in that a given piece
of code should either contain or not contain a semantic dependency
independent of the implementation used to run it.

>>>>

Semantic dependency is a notoriously difficult concept to define
rigorously and precisely.
A large part of the reason is because it was never a completely clear
concept to begin with, especially when there are multiple accesses to
the variables involved.
In this section we will stick our necks out by offering just such a
definition.
No doubt many people will object to it for various reasons, but we
nevertheless hope it will help move the discussion forward.

@@

A drawback of the definition is that it is only relative to a specific
compiler or implementation.
This may strike some people as too restrictive, in that a given piece
of code should either contain or not contain a semantic dependency
independent of the implementation used to run it.
